---
title: "Week 4 homework assignment"
author: Student Name
date: Due Date
output: github_document
editor_options:
  chunk_output_type: inline
---

## DSI-EDA
## Professor Cassy Dorff

## STEPS:

(1) Read the following article (it is for data purposes!)

NPR "CHART: The Relationship Between Seeing Discrimination And Voting For Trump"
- [link here](https://www.npr.org/2017/08/18/544265493/chart-the-relationship-between-seeing-discrimination-and-voting-for-trump)
- [even more information on the data here](https://www.prri.org/research/americans-views-discrimination-immigrants-blacks-lgbt-sex-marriage-immigration-reform/)
(2) Your goal is to recreate the graphic titled "Perceptions Of Discrimination Track Closely With Voting Against Trump." Data for analysis is in the "week4-hw-data.csv" file. Note that this data is from a different version of the PRRI survey, and the results won't match the NPR graph exactly.

(3) Graphic replication: You should:
1. Create an .rmd file to show your analysis. Write 1 sentence for each block of code, explaining what you do in that line of code.
2. Identify and prepare the variables of interest (you may need to group, summarize, or rename variables to reflect the NPR chart.)
3. Next recreate the graphic using ggplot. Recreate everything *except*:
  - the labels that are on California and Wyoming.
  - the colors (you can choose your own or use the same as the article)
4. This means your plot should have the same labels on the axes, gridlines, etc.
5. Is there anything misleading about the graphic? Why or why not?
6. You can give your colleagues "hints" but do *not* give them the code for reproducing the graphic. That breaks our honor code since I asked you not to do it!

(4) What do you think about this graphic? Do you think this relationship exists? Why or why not, in your own words?

(5) Make one additional graphic of your choice using this data. Write 3-5 sentences in clear, plain language about what the graphic illustrates about the data.


## Part 2

Previously, we explored data about wine. 

1. Make a barplot with the wine data to explore our original question about the relationship between alcohol content and quality. Why might a simple bar plot be misleading here? (Read a bit about geom_bar first, if needed)


```{r}
#answer

```

2. A lot of the hardwork in learning R skills is learning how to read helpfiles and use stackoverflow on your own. I showed you a glimpse of information about themes in class. Use the code below to make additional changes. This might take a bit of digging and reading about these graphical components online. Specifically, can you figure out how to (try to complete 2 out of 4):

* get rid of panel border completely and keep the grid lines?
* put the legend on the top or bottom?
* capitalize the legend name appropriately?
* add units for alcohol content and wine quality (if applicable)?

```{r}
ggplot(winequality_red, aes(x=quality, y= alcohol)) +
      geom_jitter(aes(col=`fixed acidity`)) +
      scale_color_viridis(option = "D", direction = -1, alpha = .6) +
      labs(title="Alcohol Content, Fixed Acidity and Wine Quality", y="Alcohol Content", x="Wine Quality")  +
      theme_bw()
```


2. Explain in 1-3 sentences what we can learn from our wine graphic produced in class.

Answer: 


